Response to Reviewers' Comments

### 2025-02-05 review/review.tex
Add proof for intersection

\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}

% Define the custom color
\definecolor{answercolor}{rgb}{0.35,0.47,0.28}

@@

    \answer{}

@@

>>>>

\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\newtheorem{theorem}{Theorem}
% Define the custom color
\definecolor{answercolor}{rgb}{0.35,0.47,0.28}

@@

	      \answer{Thanks for your remarks that has given us plenty to think about. We have answered to this remarks in a dedicated Section \ref{sec:evaluation_of_the_number_of_iterations_for_convergence} at the end of this document.}

@@

\appendix

\section{Sketch of Proof Mesh-Height Map Intersection}
\label{sec:sketch_of_proof_mesh_height_map_intersection}

The question on the "stability" of the intersection between $M$ and the water height can be divided into two questions:

\subsection{Dimension of the Intersection}

First, does the intersection between $M$ and the water height (the height map) always result in some loop (or empty/singleton set), but not in some open loop or a stranger subset of $\mathbb{R}^3$? This question is non-trivial and can be summarized with the following theorem:

\begin{theorem}
	Let $M$ be a compact 2-manifold without any border (our mesh) and
	\begin{equation}
		H=\{(x,y,z) \in \mathbb{R}^3 \mid h(x,z)-y=0\},
	\end{equation}
	then $M \cap H$ can only be:
	\begin{enumerate}
		\item Empty,
		\item $x \in \mathbb{R}^3$,
		\item $\cup_i c_i$ where $c_i$ are homeomorphic sets to the unit circle $S^1$.
	\end{enumerate}
\end{theorem}

The proof of this theorem is a bit long and out of scope for this paper, as it requires some skills in differential topology, but here is a sketch of a demonstration:

The idea of the proof is to characterize the dimension of the intersection and to prove that the intersection is always compact. Since compact sets of dimension one in $\mathbb{R}^3$ are homeomorphic to a finite union of circles, this will establish the claim.

First, note that the compactness of the intersection is quite trivial, as by definition $M$ is compact and $H$ is by definition closed, therefore their intersection must be compact.

Second, determining the dimension is a bit more complex. However, we can take advantage of the \textit{\href{https://en.wikipedia.org/wiki/Preimage_theorem}{preimage theorem}}, which under certain conditions provides a characterization of the dimension of a set. Consequently, our objective is to pose the problem in a way that allows us to apply the preimage theorem.

Define the function:
\begin{equation}
	f: M \to \mathbb{R}, \quad f(x,z,y) \mapsto h(x,z)-y.
\end{equation}
Note that $S \cap H$ is equal to $f^{-1}(0)$. Moreover, by the definition of $h$ and its linearity, $f$ is a smooth map.

Now, we need to prove that $0$ is a regular value of $f$, that is, $\forall x \in f^{-1}(0)$, the differential
\begin{equation}
	df_x : T_x M \to T_0 \mathbb{R} \simeq \mathbb{R}
\end{equation}
is surjective. To rule out the trivial case, let us directly assume that $f^{-1}(0) \neq \emptyset$. Moreover, we have:
\begin{equation}
	df_x(v) = \nabla f \cdot v.
\end{equation}
Note that if $df_x$ is not the zero map, then $df_x$ is surjective (indeed, if it is not a zero map, then $\text{im}(df_x) = \mathbb{R}$, because it cannot be the trivial vector subspace $\{0\}$). Therefore, we have two cases:

\begin{enumerate}
	\item If $T_x M \subset T_x H$, then $df_x$ is not the zero map, which corresponds to the intersection being a single point.
	\item If $T_x M$ is not a subset of $T_x H$, then $df_x$ is not the zero map and thus surjective.
\end{enumerate}

By applying the preimage theorem, we obtain:
\begin{equation}
	\text{codim}(f^{-1}(0)) = \dim(\mathbb{R}) = 1.
\end{equation}
Moreover, since we are in finite dimensions:
\begin{equation}
	\text{codim}(f^{-1}(0)) = \dim(M) - \dim(f^{-1}(0)).
\end{equation}
This concludes the demonstration by giving us:
\begin{equation}
	\dim(S \cap H) = 1.
\end{equation}

\subsection{Intersection Degenerate}

Second, as you mentioned, does the projection on the $zx$ plane cause the intersection polygons to be self-intersected? To address this, let us simply remark that if the polygon is simple on the continuous height map, then the projection, which only alters the vertical component, should also yield a simple polygon. This would not be the case if instead of a height map we were using more complex parametric surfaces, where two points of the surface could be projected onto the same point of the $xz$ plane. The key point here is the bijection between the $xz$ plane and the height map.
